Urban Heat Risk Mapping Using Multiple Point Patterns in Houston, Texas

### 2016-12-13 reviewer_response.tex

We responded to this comment by adding the following text to the article:

\begin{displayquote}
A potential solution to avoid realigning the census data to the grid cells is to let the census block groups equal the $\mathcal{G}_k$ denoted in (2) rather than the grid cells. However, the heat information used in this research (described in detail in Section 3.1) is provided at a 1-km$^2$ resolution and these grid cells were chosen to align exactly with the available heat data. Using the block groups in place of the grid cells would necessitate aligning the heat information to the census block group areas. Because heat is our primary variable of interest we prefer realigning the demographic information to the grid associated with the heat data as opposed to the alternative. Therefore, we proceed having aligned the population data as described.
\end{displayquote}

\item\textit{Heat enters as an upper level covariate, with ecological fallacy risks?   Are the census data not available to study how some of these features vary with key other demographics?   I appreciate all the census data are disclosure limited but some multiway information on air conditining and age band could really limit the potential problems with confounders in the aggregate analysis.}

In order to address this concern, we examined the impact of additional demographic covariates from the census data on our model. We also included all two-way interaction terms between the various covariates as potential predictors in our model in order to mitigate the potential problems with confounders (see Table 2), as suggested by the reviewer.
